### 2020-07-20 code/figure1.Rmd
adjust plot so legend does not bleed to adjacent plot. fixed E and F not scaled to rest of umap plots. added 50 samples with NA values in the front and back to prevent points touching y-axis

@@

####################
## Figure 1B data ##
####################
gdc_path <- gdc_reactome_path_analysis %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column(var = "sample") %>% ## move path_names to column
  .[match(rownames(tumor_samples), .$sample), ]

gdc_path_mca <- left_join(gdc_path, tumor_samples[, c(1, 3)],
  by = c("sample" = "submitted_sample_id")) %>%
  column_to_rownames(var = "sample")

gdc_path_sample_names <- rownames(gdc_path_mca)
gdc_path_tumor_types <- gdc_path_mca$project_code.x

gdc_path_mca$project_code.x <- NULL

## create a categorical variable from the boolean variable
pathway_list <- make_clean_names(colnames(gdc_path_mca))
pathway_count <- length(pathway_list)
gdc_path_mca <- as.data.frame(lapply(gdc_path_mca, function(x) {
  factor(x, levels = c(0, 1), labels = c("no", "yes"))
}))
colnames(gdc_path_mca) <- pathway_list
gdc_path_mca$project_code <- gdc_path_tumor_types
rownames(gdc_path_mca) <- gdc_path_sample_names

## perform mca
mca_res <- MCA(X = gdc_path_mca[, pathway_list], graph = FALSE)

expl_var <- mca_res$eig[, 2]
expl_var_perm <- matrix(NA, ncol = length(mca_res$eig[, 2]), nrow = 100)

set.seed(4242)
for (k in seq(100)) {
  gdc_perm <- as.data.frame(lapply(gdc_path_mca[, pathway_list], sample))
  MCA_perm <- MCA(X = gdc_perm, graph = FALSE)
  expl_var_perm[k, ] <- MCA_perm$eig[, 2]
}

randomize <- tibble(
  eigenvalue = 1:length(expl_var),
  expl_var = expl_var,
  perm = colMeans(expl_var_perm),
  pvalue = rowSums(t(expl_var_perm) >= expl_var) / 100
)

optimal_mca_dimensions <- randomize %>%
  filter(pvalue < 0.05) %>%
  filter(eigenvalue == max(eigenvalue)) %>%
  pull(eigenvalue)

mca_res <- MCA(
  X = gdc_path_mca[, pathway_list],
  ncp = optimal_dimensions, graph = FALSE
)

save(randomize, mca_res, file = "figure1B_data.rda")

####################
## Figure 1C data ##
####################
rng <- RNGseq(max_n_pt * n_iter, 42)
r <- rng[[3649]]

rngtools::setRNG(r)
gdc.umap <- uwot::umap(mca_res$ind$coord, 
                       n_components = 3,
                       n_neighbors = round(sqrt(nrow(mca_res$ind$coord))), # 87
                       n_epochs = 1000,
                       n_threads = 1)
gdc_umap_coors <- as.data.frame(gdc.umap) %>%
  rename(plot_x = V1, plot_y = V2, plot_z = V3)

####################
## Figure 1D data ##
####################
n_iter <- 40
max_n_pt <- 200
score_mca <- matrix(as.numeric(NA), nrow = max_n_pt - 2, ncol = n_iter)

n_tumors <- nrow(mca_res$ind$coord)

cl <- makeCluster(8)
registerDoParallel(cl)

for (i in 3:max_n_pt) {
  print(paste0("MIN POINTS = ", i))
  score_iter <- foreach(1:n_iter,
    .combine = c,
    .export = c("mca_res"),
    .packages = c("dbscan", "uwot"),
    r = rng[(i - 1) * n_iter + 1:n_iter]
  ) %dopar% {
    rngtools::setRNG(r)
    umap_init_mca <- umap(mca_res$ind$coord, 
                          min_dist = 1e-6, 
                          n_components = 3, 
                          n_neighbors = round(sqrt(nrow(mca_res$ind$coord))), 
                          n_epochs = 1000, 
                          n_threads = 1)
    res <- hdbscan(umap_init_mca, minPts = i)
    score_iter_temp <- sum(res$membership_prob < 0.05) / n_tumors
    return(score_iter_temp)
  }
  score_mca[i - 2, ] <- score_iter
}

score <- rowMeans(score_mca)
score_df <- tibble(minPts = 3:max_n_pt, score = score)

sample_df <- score_mca %>%
  as.data.frame() %>%
  as_tibble() %>%
  add_column(minPts = 3:max_n_pt, .before = 1) %>%
  pivot_longer(-minPts) %>%
  group_by(minPts)

optimal_minPts <- score_df %>%
  filter(score == min(score)) %>%
  pull(minPts)

save(score_df, sample_df, optimal_minPts, file = "optimal_minpts_score.rda")

@@

```{r fig-1a-1l, warning=FALSE, fig.height=11, fig.width=8.5, message = FALSE}
load("../data/cancer_disrupt_heatmap.Rda")
umap_cancertype <- fread("../data/umap_2d_3d_coors.tsv")

@@

fig1A <- ggplot(data = cancer_disrupt_heatmap, aes(y=sample_id, x=path_name, fill = membership)) + 
  geom_tile(size = 0.6) +
  scale_fill_manual(values = c("grey", "firebrick3")) +
  facet_grid(type ~ ., scales = "free", space = "free", switch = "y") +
scale_y_discrete(position = "left") +
  labs(tag = "A") +
  ylab("") +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        strip.text.y = element_text(size = 12, hjust = 0),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_blank(),
        legend.position = "none")

@@

optimal_mca_dimensions <- randomize %>%
  filter(pvalue < 0.05) %>%
  filter(eigenvalue == max(eigenvalue)) %>%
  pull(eigenvalue)

permut_p <- randomize %>%
  filter(eigenvalue < 50) %>%
  ggplot(aes(x = eigenvalue, y = expl_var / 100)) +
  geom_line(aes(colour = "#998ec3")) +
  geom_line(aes(y = perm / 100, colour = "#f1a340")) +
  scale_color_identity(guide = guide_legend(title = ""), 
                       labels = c("Eigenvalues", "Permuted Eigenvalues")) +
  scale_y_continuous(labels = scales::percent) +
  xlab("MCA Eigenvalues") +
  ylab("explained variance") +
  theme_classic()

pvalue_p <- randomize %>%
  filter(eigenvalue < 50) %>%
  ggplot(aes(x = eigenvalue, y = pvalue)) +
  geom_line() +
  geom_point() +
  geom_vline(xintercept = optimal_dimensions, color = "red") +
  ggtitle(label = "", subtitle = paste0("Significant dimensions = ", optimal_dimensions)) +
  xlab("MCA Eigenvalues") +
  ylab("P-value") +
  theme_classic()

fig1B <- permut_p /
  pvalue_p + plot_annotation(title = "Significance of MCA Eigenvalues")

## umap monochrome 2d
fig1C <- ggplot(umap_cancertype, aes(x=x_2d, y=y_2d)) +
  geom_point(colour = "grey", size = 0.25) +
  xlab("umap_1") +
  ylab("umap_2") +
  theme_classic() +
  labs(tag = "C") +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank())
## umap hdb_scan
fig1E <- ggplot(subset(umap_cancertype, clust !=0), aes(x = x_2d, y = y_2d, color = as.factor(clust))) +
  geom_point(data = umap_cancertype, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(size = 0.25) + scale_color_manual(values = kelly.colours[-c(1:2)]) +
  guides(color = F) +
  theme_classic() +
  xlab("umap_1") +
  ylab("umap_2") +
  theme_classic() +
  labs(tag = "E") +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank())

## umap knn_clust 
fig1F <- ggplot(subset(umap_cancertype), aes(x = x_2d, y = y_2d, color = as.factor(knn_clust))) +
  geom_point(size = 0.25) + scale_color_manual(values = kelly.colours[-c(1:2)]) +
  guides(color = F) +
  theme_classic() +
  xlab("umap_1") +
  ylab("umap_2") +
  theme_classic() +
  labs(tag = "F") +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank())

@@

fig1G <- ggplot(mut_order, aes(x = V1, y = log10mut, color = knn_clust)) + 
  geom_point(size = 0.25) + 
  ylab("Log10(Mutation Count)") + 
  xlab("") +
  labs(tag = "G") +
  theme_classic() +
  facet_wrap(~ factor(knn_clust, levels = c(1:12)), ncol = 12, scales = "free_x") +
  geom_hline(data= mut_median, aes(yintercept=mut_med)) +
  scale_y_continuous(sec.axis = sec_axis(~.)) + ## dup y-axis
  scale_x_discrete(breaks = c(as.character(mut_order$V1[300]), as.character(xaxis_breaks$V1)), labels = c("n =" ,total_n$Freq)) +
  theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks.x = element_blank(),
        axis.line.x = element_line(colour = "black", size = 0.5),
        axis.line.x.top = element_line(colour = "black", size = 0.5),
        #strip.background.x = element_blank(),
        strip.placement = "outside",
        strip.text.x = element_text(size = 12),
        legend.position = "none") +
  scale_color_manual(values = kelly.colours[-c(1:2)])

@@

## umap by cancer type
fig1H <- ggplot(umap_cancertype[umap_cancertype$project_code %in% c("COAD", "BRCA", "HNSC", "PAAD"),], aes(x = x_2d, y = y_2d, colour = project_code)) +
  geom_point(data = umap_cancertype, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(size = 0.25) + 
  theme_classic() +
  ylab("umap_2") +
  xlab("umap_1") +
  labs(tag = "H", color = "") +
  scale_color_manual(labels = c("BRCA", "COAD", "HNSC", "PAAD"), 
                     values = c('#fb9a99', '#b15928', '#6a3d9a', 'springgreen4')) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "bottom")

## umap of brca subtype
fig1I <- ggplot(umap_cancertype %>% filter(project_code == "BRCA" & !is.na(Subtype_Selected)), aes(x = x_2d, y = y_2d, colour = Subtype_Selected)) +
  geom_point(data = umap_cancertype, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(size = 0.25) +
  theme_classic() +
  ylab("umap_2") +
  xlab("umap_1") +
  labs(tag = "I", color = "") +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "bottom")

@@

fig1J <- ggplot(brca %>% filter(mut_type != "NA"), aes(x = x_2d, y = y_2d, colour = mut_type)) +
  geom_point(data = brca, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(size = 0.25) + 
  theme_classic() +
  ylab("umap_2") +
  xlab("umap_1") +
  labs(color = "", tag = "J") +
  scale_color_manual(labels = c("BRCA1", "BRCA1,BRCA2", "BRCA2"), 
                     values = c('#33a02c', '#e31a1c', '#ff7f00')) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "bottom")

## umap stage
fig1K <- ggplot(subset(umap_cancertype, ajcc_pathologic_tumor_stage != "Not Available"), aes(x = x_2d, y = y_2d, colour = ajcc_pathologic_tumor_stage)) +
  geom_point(data = umap_cancertype, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(size = 0.25) + 
  theme_classic() +
  ylab("umap_2") +
  xlab("umap_1") +
  labs(tag = "K", color = "") +
  scale_color_manual(labels = c("Stage I", "Stage II", "Stage III", "Stage IV"), 
                     values = c('darkgoldenrod3','dodgerblue3','yellow3','tomato2')) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "bottom")

## umap metastasis
fig1L <- ggplot(umap_cancertype, aes(x = x_2d, y = y_2d)) +
  geom_point(data = umap_cancertype, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(data = subset(umap_cancertype, ajcc_metastasis_pathologic_pm == "M0"), aes(x = x_2d, y = y_2d, colour = ajcc_metastasis_pathologic_pm), size = 0.25) + 
  geom_point(data = subset(umap_cancertype, ajcc_metastasis_pathologic_pm == "M1"), aes(x = x_2d, y = y_2d, colour = ajcc_metastasis_pathologic_pm), size = 0.25) + 
  ylab("umap_2") +
  xlab("umap_1") +
  labs(tag = "L", color = "") +
  scale_color_manual(labels = c("M0", "M1"), 
                     values = c('#a6cee3','#1f78b4')) +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "bottom")

layout <- '
AAAABBCCDD
AAAAEEEFFF
AAAAGGGGGG
AAAAGGGGGG
AAAAHHIIJJ
AAAAKKLL##
'

fig1A + plot_spacer() + fig1C + plot_spacer() + fig1E + fig1F + fig1G + fig1H + fig1I + fig1J + fig1K + fig1L + plot_layout(design = layout)

>>>>

---
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r}
library(data.table)
library(ggplot2)
library(ggplotify)
library(tidyverse)
library(grid)
library(patchwork)
```

@@

####################
## Figure 1C data ##
####################
gdc_path <- gdc_reactome_path_analysis %>% t() %>% as.data.frame() %>%
  rownames_to_column(var = "sample") %>% ## move path_names to column
  .[match(rownames(tumor_samples), .$sample),]

## umap analysis
set.seed(3296)
gdc.umap <- umap(gdc_path[,2:length(gdc_path)]) ## default n_component is 2
gdc_umap_coors <- data.frame(x_2d = gdc.umap$layout[,1], y_2d = gdc.umap$layout[,2])

@@

```{r fig-1a-1l, warning=FALSE, fig.height=15, fig.width=16, message = FALSE}
load("../data/cancer_disrupt_heatmap.Rda")
umap_cancertype <- fread("../data/umap_2d_3d_coors.tsv")

@@

fig1A <- ggplot(data = cancer_disrupt_heatmap, aes(y=sample_id, x=path_name, fill = membership)) + 
  geom_tile(size = 0.6) +
  scale_fill_manual(values = c("grey", "firebrick3")) +
  facet_grid(type ~ ., scales = "free", space = "free", switch = "y") +
scale_y_discrete(position = "left") +
  ylab("") +
  xlab("377 Reactome Pathways") +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        strip.text.y = element_text(size = 12, hjust = 0),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_blank(),
        legend.position = "none")

@@

## umap monochrome 2d
fig1C <- ggplot(umap_cancertype, aes(x=x_2d, y=y_2d)) +
  geom_point(colour = "grey", size = 0.25) +
  xlab("umap_1") +
  ylab("umap_2") +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank())
## umap hdb_scan
fig1E <- ggplot(subset(umap_cancertype, clust !=0), aes(x = x_2d, y = y_2d, color = as.factor(clust))) +
  geom_point(data = umap_cancertype, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(size = 0.25) + scale_color_manual(values = kelly.colours[-c(1:2)]) +
  guides(color = F) +
  theme_classic() +
  xlab("umap_1") +
  ylab("umap_2") +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank())

## umap knn_clust 
fig1F <- ggplot(subset(umap_cancertype), aes(x = x_2d, y = y_2d, color = as.factor(knn_clust))) +
  geom_point(size = 0.25) + scale_color_manual(values = kelly.colours[-c(1:2)]) +
  guides(color = F) +
  theme_classic() +
  xlab("umap_1") +
  ylab("umap_2") +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank())

@@

## Need to add 50 pseudo samples front and end of data so they don't touch the y-axis
mut_order <- mut_order[,c("V1", "knn_clust", "log10mut")] ## selecting relevant column

begin_NA <- data.frame(V1 = paste0("sample", 1:50), 
                       knn_clust = min(as.numeric(mut_order$knn_clust)), ## put lowest cluster to prevent a new facet
                       log10mut = NA) ## put NA values so they don't get plotted
end_NA <- data.frame(V1 = paste0("sample", 51:100), ## repeat the step for the ends
                       knn_clust = max(as.numeric(mut_order$knn_clust)),
                       log10mut = NA)
mut_order <- rbind(begin_NA, mut_order, end_NA) ## rbind the data in a specfic order

mut_order$V1 <- factor(mut_order$V1, levels = mut_order$V1) ## factor samples
mut_order$knn_clust <- factor(mut_order$knn_clust, levels = c(1:12)) ## factor clusters
#### test ####

fig1G <- ggplot(mut_order, aes(x = V1, y = log10mut, color = knn_clust)) + 
  geom_point(size = 0.25) + 
  ylab("Log10(Mutation Count)") + 
  xlab("") +
  theme_classic() +
  facet_wrap(~ factor(knn_clust, levels = c(1:12)), ncol = 12, scales = "free_x") +
  geom_hline(data= mut_median, aes(yintercept=mut_med)) +
  scale_y_continuous(sec.axis = sec_axis(~.)) + ## dup y-axis
  scale_x_discrete(breaks = c(as.character(mut_order$V1[1]), as.character(xaxis_breaks$V1)), labels = c("n =" ,total_n$Freq)) +
  theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks.x = element_blank(),
        axis.line.x = element_line(colour = "black", size = 0.5),
        axis.line.x.top = element_line(colour = "black", size = 0.5),
        panel.spacing = unit(1, "lines"),
        strip.background = element_rect(size = 0.5),
        strip.placement = "outside",
        strip.text.x = element_text(size = 10),
        legend.position = "none") +
  scale_color_manual(values = kelly.colours[-c(1:2)])

@@

## umap by cancer type
fig1H <- ggplot(umap_cancertype[umap_cancertype$project_code %in% c("COAD", "BRCA", "HNSC", "PAAD"),], aes(x = x_2d, y = y_2d, colour = project_code)) +
  geom_point(data = umap_cancertype, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(size = 0.25) + 
  theme_classic() +
  ylab("umap_2") +
  xlab("umap_1") +
  labs(color = "") +
  scale_color_manual(labels = c("BRCA", "COAD", "HNSC", "PAAD"), 
                     values = c('#fb9a99', '#b15928', '#6a3d9a', 'springgreen4')) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "bottom")

## umap of brca subtype
fig1I <- ggplot(umap_cancertype %>% filter(project_code == "BRCA" & !is.na(Subtype_Selected)), aes(x = x_2d, y = y_2d, colour = Subtype_Selected)) +
  geom_point(data = umap_cancertype, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(size = 0.25) +
  theme_classic() +
  ylab("umap_2") +
  xlab("umap_1") +
  labs(color = "") +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "bottom")

@@

fig1J <- ggplot(brca %>% filter(mut_type != "NA"), aes(x = x_2d, y = y_2d, colour = mut_type)) +
  geom_point(data = brca, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(size = 0.25) + 
  theme_classic() +
  ylab("umap_2") +
  xlab("umap_1") +
  labs(color = "") +
  scale_color_manual(labels = c("BRCA1", "BRCA1,BRCA2", "BRCA2"), 
                     values = c('#33a02c', '#e31a1c', '#ff7f00')) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "bottom")

## umap stage
fig1K <- ggplot(subset(umap_cancertype, ajcc_pathologic_tumor_stage != "Not Available"), aes(x = x_2d, y = y_2d, colour = ajcc_pathologic_tumor_stage)) +
  geom_point(data = umap_cancertype, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(size = 0.25) + 
  theme_classic() +
  ylab("umap_2") +
  xlab("umap_1") +
  labs(color = "") +
  scale_color_manual(labels = c("Stage I", "Stage II", "Stage III", "Stage IV"), 
                     values = c('darkgoldenrod3','dodgerblue3','yellow3','tomato2')) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "bottom")

## umap metastasis
fig1L <- ggplot(umap_cancertype, aes(x = x_2d, y = y_2d)) +
  geom_point(data = umap_cancertype, aes(x = x_2d, y = y_2d), colour = "grey", size = 0.25) +
  geom_point(data = subset(umap_cancertype, ajcc_metastasis_pathologic_pm == "M0"), aes(x = x_2d, y = y_2d, colour = ajcc_metastasis_pathologic_pm), size = 0.25) + 
  geom_point(data = subset(umap_cancertype, ajcc_metastasis_pathologic_pm == "M1"), aes(x = x_2d, y = y_2d, colour = ajcc_metastasis_pathologic_pm), size = 0.25) + 
  ylab("umap_2") +
  xlab("umap_1") +
  labs(color = "") +
  scale_color_manual(labels = c("M0", "M1"), 
                     values = c('#a6cee3','#1f78b4')) +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.ticks = element_blank(),
        legend.position = "bottom")

empty_plot <- ggplot() + theme_void()

layout <- '
AAAABBBCCCDDD
AAAAEEEFFF###
AAAAGGGGGGGGG
AAAAGGGGGGGGG
AAAAHHHIIIJJJ
AAAAKKKLLL###
'

fig1A + empty_plot + fig1C + empty_plot + fig1E + fig1F + fig1G + fig1H + fig1I + fig1J + fig1K + fig1L + plot_layout(design = layout) + plot_annotation(tag_levels = 'A')
